Wavelets

### 2019-02-18 wavelets.Rmd
fixedBits

Working with remotely-sensed SST and *in-situ* collected coastal seawater temperature, in the analyses bellow I aim to show how the intensity and duration of upwelling events varies. It is important to remember that each of the datasets used within this study obtained SSTs at different resolutions. Here i was only required to plot a time series of 1year.

@@

```{r}
one_year <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

SACTN_1yr_US1 <- one_year(df = overlap_ts) 
MUR_1yr_US1 <- one_year(df = insitu_MUR) 
OISST_1yr_US1 <- one_year(df = insitu_OISST) 
G1SST_1yr_US1 <- one_year(df = insitu_G1SST) 
K10_1yr_US1 <- one_year(df = insitu_K10) 
```

@@

```{r}
temp.d <- function(df){
temp.d <- df %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(temp, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)
}

o
temp.d <- temp.d(df = overlap_ts) 
# temp.d <- temp.d(df = insitu_MUR) 
# temp.d <- temp.d(df = insitu_OISST) 
# temp.d <- temp.d(df = insitu_G1SST) 
# temp.d <- temp.d(df = insitu_K10)

@@

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wavelet.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```

>>>>

Working with remotely-sensed SST and *in-situ* collected coastal seawater temperature, in the analyses bellow I aim to show how the intensity and duration of upwelling events varies per sites along the west coast of South Africa. It is important to remember that each of the datasets used within this study obtained SSTs at different resolutions. Here i was only required to plot a time series of 2 years.

@@

```{r}
filtered_years <- function(df){
  upwelling<- df %>% 
  filter(year(date) %in% seq(2014, 2015)) %>% 
  drop_na()
}

SACTN_fyears <- filtered_years(df = overlap_ts) 
MUR_fyears <- filtered_years(df = insitu_MUR) 
OISST_fyears <- filtered_years(df = insitu_OISST) 
G1SST_fyears <- filtered_years(df = insitu_G1SST) 
K10_fyears <- filtered_years(df = insitu_K10) 
```

@@

```{r}

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
# SACTN_fyears <- SACTN_fyears %>% 
#   dplyr::rename(temp = insitu_temp)

temp.d <- function(df){
temp.d <- df %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(temp, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)
}

# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
temp.d <- temp.d(df = K10_fyears)

@@

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```
